---
title: "data_glance"
date: "10/9/2018"
output: html_document
---

```{r}
#install.packages("tidyverse")
library(tidyverse)
library(dplyr)
```

```{r}
library(readxl) ## reading the excel 
library(stringr)
listings <- read_excel("Clb.xlsx", skip = 1) #from albert 
listings_numerical <- read.csv("Clb_numerical.csv",skip=1)

```

##### data cleaning 
###### getting park out of amenities
```{r}
data_raw <- listings %>%
select(neighbourhood_cleansed,room_type,accommodates,square_feet,extra_people,minimum_nights,instant_bookable, amenities, price) %>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace")) #in caps or not  
  

#one hot coding
#for loop val in c("TV....")
```


###### getting rid of dollar signs

```{r}

data_cleaned <- data_raw %>%  #from albert
  mutate(
    price = str_replace_all(price, "\\$", ""),
    price = str_replace_all(price, ",", ""),
    price = as.numeric(price)
    )
#change all factor to numerical in listings_numerical
listings_numerical_cleaned <- listings_numerical %>%
  mutate(
    price = as.numeric(price),
    weekly_price= as.numeric(weekly_price),
    monthly_price = as.numeric(monthly_price),
    security_deposit = as.numeric(security_deposit),
    cleaning_fee  = as.numeric(cleaning_fee ),
    extra_people = as.numeric(extra_people),
    zipcode = as.numeric(zipcode),
    host_response_rate = as.numeric(host_response_rate)
    )
  
```

##### price become price/max commodate

```{r}
data_cleaned <- data_cleaned %>%
  mutate(price_per_p = price/accommodates)
```

##### regression models with all

```{r}
cor_data <-  data_cleaned %>% 
  select(accommodates,extra_people,minimum_nights,price_per_p) #only on numerical
cor(cor_data)
```


```{r}
mod1 <- lm(price_per_p~ instant_bookable + minimum_nights + room_type+ neighbourhood_cleansed + extra_people, data_cleaned) #when square feet added, no one is significant lol
#Jeez.... that's bad
summary(mod1)
```

```{r}
mod2 <- lm(price_per_p ~ instant_bookable + room_type+ neighbourhood_cleansed + extra_people, data_cleaned)
summary(mod2)
```

--------------------------------------------------------------------------------------
# Using the . in the formula interface includes all non-response variables in the data frame.

```{r}
# mean price of the accomodation by district
MeanP_by_district <- data_cleaned %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(price_per_p = mean(price_per_p))

#Histogram of mean price

ggplot(MeanP_by_district,
       mapping = aes(x = neighbourhood_cleansed, y = price_per_p)) + geom_col() +
       coord_flip() 

#Boxplot of the median price for each district

ggplot(data_cleaned, aes(x = neighbourhood_cleansed, y = price_per_p))  +
  geom_boxplot() +
  scale_y_log10() + coord_flip()
  
```
<<<<<<< HEAD
 
```{r}
#mutate number of listings sorted by area
 neighbourhood_data<-data_cleaned %>% 
  group_by(neighbourhood_cleansed) %>% 
  summarize(number_listings=n()) 

ggplot(neighbourhood_data, aes(x = neighbourhood_cleansed, y = number_listings))  +
  geom_col() + coord_flip()
```


=======
#### albert plot
```{r}
ggplot(data_cleaned, aes(x=price_per_p)) +
  geom_histogram() +
  scale_x_log10()

ggplot(data_cleaned, aes(x=room_type, y =price_per_p))  + 
  geom_boxplot() + 
  scale_y_log10()

lm(price_per_p~room_type, data = data_cleaned) %>% summary()
```
>>>>>>> b48823d313f5c56639a0a6300d86e87e6bb4e9b1

```{r}
# Run .null on all numerical and Catergorical Data
mfull <- lm(price ~ ., data=listings_numerical)

```


# Using the .to includes all non-response variables in the data frame
