---
title: "data_glance"
date: "10/9/2018"
output: html_document
---

```{r}
library(tidyverse)
library(readxl)
library(stringr)
library(dplyr)
library(mice)
```

```{r}
listings <- read_excel("Clb.xlsx", skip = 1)%>%
  mutate(price_per_p = price/accommodates) #all variables, 97. from albert + mutated price 
listings_numerical <- read_excel("Clb_numerical.xlsx", skip=1) %>%
select(-(cancellation_policy))%>%
  mutate(price_per_p = price/accommodates)# all numerical variables, 35 
```

##### data cleaning 

```{r}
listings_amenities <- listings %>% # contains only amenities 
select(neighbourhood_cleansed,room_type,accommodates,instant_bookable, amenities, price) %>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace"),
         price_per_p = price/accommodates)  
  
```

##### regression models with all

```{r}
#only on numerical
cor_data <- listings_numerical %>%
  select(-c(latitude, longitude,host_response_rate))# get rid of chr
# need to get rid of N/A, albert?


cor_test <- listings_numerical%>%
  select(price_per_p,extra_people,bedrooms,host_listings_count,bathrooms, beds, weekly_price, number_of_reviews,security_deposit,minimum_nights)
cor(cor_test)
```
--------------------------------------------------------------------------------------
# Using the . in the formula interface includes all non-response variables in the data frame.

# interpretation 
```{r}
# mean price of the accomodation by district
MeanP_by_district <- listings %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(price_per_p = mean(price_per_p))

#Histogram of mean price

ggplot(MeanP_by_district,
       mapping = aes(x = neighbourhood_cleansed, y = price_per_p)) + geom_col() +
       coord_flip() 
#suburbs have the highest average pricing 

#Boxplot of the median price for each district

ggplot(listings, aes(x = neighbourhood_cleansed, y = price_per_p))  +
  geom_boxplot() +
  scale_y_log10() + coord_flip()
# The range of price for the center districts are most stable, in terms of variability.
# Where as, this is not the case for the suburbs, despite the fact that they have similar median.
# According to the graph, we realize that it is important to know what varaibles predict the 
# price.
  
```

```{r}
#mutate number of listings sorted by area
 neighbourhood_data<-listings %>% 
  group_by(neighbourhood_cleansed) %>% 
  summarize(number_listings=n())

ggplot(neighbourhood_data, aes(x = neighbourhood_cleansed, y = number_listings))  +
  geom_col() + coord_flip()
```
# top four most popular districts: ChaoYang, DongCheng, Haidian, Xichen.

#### albert plot
```{r}
ggplot(listings, aes(x=price_per_p)) +
  geom_histogram()+
  scale_x_log10() # if not looking at the outliers, almost normal distribution
# center around 200-300 rmb per person per night 

ggplot(listings, aes(x=room_type, y =price_per_p))  + 
  geom_boxplot() + 
  scale_y_log10()
# entire home/apt is more expensive than private room then shared room, but not by a lot

```


--------------------------------
# getting rid of N/As
```{r}
# Run .null on all numerical and Catergorical Data
mfull <- lm(price ~ ., data=listings_numerical)
summary(mfull)
# cannot run # mean imuputation 
```

```{r}
colSums(is.na(listings_numerical)) # counting how many N/As in each column
```
Zipcode: 3983; bathrooms: 4, bedrooms:16; beds: 21; square_feet:19980; weekly_price: 19557; monthly_price: 19556; security_deposit: 12360
cleaning_fee: 11737, review_score_rating: 8259, review_scores_accuracy: 8257, review_scores_cleanliness: 8256,  review_scores_checkin:8267
review_scores_communication: 8259, review_scores_location:8281, review_scores_value: 8282, reviews_per_month:7949 

Because almost all entries in this dataset do not have square_feet, weekly_price, monthly_price, defintely dropping those three variables.

# splitting for two models, with and without reviews?

-----------------------
# MICE package 

```{r}
listings_numerical_clean <- listings_numerical%>%
  select(-c(price,square_feet, weekly_price,monthly_price,zipcode,security_deposit,
cleaning_fee, review_scores_rating, review_scores_accuracy, review_scores_cleanliness, review_scores_checkin,
review_scores_communication, review_scores_location, review_scores_value, reviews_per_month, accommodates, latitude, longitude)) #I'm dropping everything （also dropping longtitude, latitude for the ease of regression for now) with N/A, except
#bathrooms, bedrooms, and beds

```
# filling in missing bathrooms, bedrooms and beds
```{r}
tempData <- mice(listings_numerical_clean,m=5,maxit=5,meth='pmm',seed=6210) #citation
summary(tempData)
completed_listings_numerical_clean <- complete(tempData,1)
colSums(is.na(completed_listings_numerical_clean))
```


```{r}
listings_numerical_clean_head <- completed_listings_numerical_clean %>%
  head(5000)

numerical_clean_head <- lm(price_per_p ~ .,data = listings_numerical_clean_head )
summary(numerical_clean_head)
# PI, CI
```

-----------------
Another look at the NAs in the categorical datas

```{r}
colSums(is.na(listings_amenities)) # everybody else is fine except square_feet
```
#regression 

```{r}
listings_amenities_test <- listings_amenities %>%
  select(-c(amenities,accommodates, price))

mamenities_test <- lm(price_per_p ~ ., data = listings_amenities_test)
summary(mamenities_test) # small results
```






# Using the .to includes all non-response variables in the data frame: 
#Citation

citation for mice: https://datascienceplus.com/imputing-missing-data-with-r-mice-package/
for'polyreg':https://www.analyticsvidhya.com/blog/2016/03/tutorial-powerful-packages-imputing-missing-values/


#### additional code

```{r}
# data_cleaned <- data_raw %>%  #from albert
#   mutate(
#     price = str_replace_all(price, "\\$", ""),
#     price = str_replace_all(price, ",", ""),
#     price = as.numeric(price)
#     )
#change all factor to numerical in listings_numerical 
#So it kept saying that NAs introduced by coercion when I try to get rid of the dollar sign. 
```

```{r}

# listings_numerical_cleaned <- listings_numerical %>%
#   mutate(
#     price = str_replace_all(price, "\\$", ""),
#     price = str_replace_all(price, ",", ""),
#      price = as.numeric(price),
#     weekly_price= as.numeric(weekly_price),
#     monthly_price = as.numeric(monthly_price),
#     security_deposit = as.numeric(security_deposit),
#     cleaning_fee  = as.numeric(cleaning_fee ),
#     extra_people = as.numeric(extra_people),
#     zipcode = as.numeric(zipcode),
#     host_response_rate = as.numeric(host_response_rate)
#     )
  
```
