---
title: "data_glance"
date: "10/9/2018"
output: html_document
---

```{r}
library(tidyverse)
library(readxl)
library(stringr)
library(dplyr)
<<<<<<< HEAD
#install.packages("mice")
=======
>>>>>>> 3586bbf470b1579224baecd73262c07f9a3666ec
library(mice)
require(leaps)
require(mosaic)
```

```{r}
listings <- read_excel("Clb.xlsx", skip = 1)%>%
  mutate(price_per_p = price/accommodates) #all variables, 97. from albert + mutated price 
listings_numerical <- read_excel("Clb_numerical.xlsx", skip=1) %>%
select(-(cancellation_policy))%>%
  mutate(price_per_p = price/accommodates)# all numerical variables, 35 
```

##### data cleaning 

```{r}
listings_amenities <- listings %>% # contains only amenities 
select(neighbourhood_cleansed,room_type,accommodates,instant_bookable, amenities, price) %>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace"),
         price_per_p = price/accommodates)  
  
#one hot coding
#for loop val in c("TV....")
```

<<<<<<< HEAD

###### getting rid of dollar signs(merge Problem)

```{r}

data_cleaned <- data_raw %>%  #from albert
  mutate(
    price = str_replace_all(price, "\\$", ""),
    price = str_replace_all(price, ",", ""),
    price = as.numeric(price)
    )
#change all factor to numerical in listings_numerical 
#So it kept saying that NAs introduced by coercion when I try to get rid of the dollar sign. 
#listings_numerical_cleaned <- listings_numerical %>%
 # mutate(
 # price = str_replace_all(price, "\\$", ""),
 # price = str_replace_all(price, ",", ""),
 # price = as.numeric(price),
 #   #weekly_price= as.numeric(weekly_price),
   # monthly_price = as.numeric(monthly_price),
    #security_deposit = as.numeric(security_deposit),
    #cleaning_fee  = as.numeric(cleaning_fee ),
    #extra_people = as.numeric(extra_people),
    #zipcode = as.numeric(zipcode),
   # host_response_rate = as.numeric(host_response_rate)
    
  
```

##### price become price/max commodate(problem )

```{r}
data_cleaned <- data_cleaned %>%
  mutate(price_per_p = price/accommodates)
=======
>>>>>>> 384033d0d35d1b9edbf21998f52438136284db48
```

##### regression models with all

```{r}
#only on numerical
cor_data <- listings_numerical %>%
  select(-c(latitude, longitude,host_response_rate))# get rid of chr
# need to get rid of N/A, albert?


cor_test <- listings_numerical%>%
  select(price_per_p,extra_people,bedrooms,host_listings_count,bathrooms, beds, weekly_price, number_of_reviews,security_deposit,minimum_nights)
cor(cor_test)
```
--------------------------------------------------------------------------------------
# Using the . in the formula interface includes all non-response variables in the data frame.

=======
>>>>>>> 3586bbf470b1579224baecd73262c07f9a3666ec
# interpretation 
```{r}
# mean price of the accomodation by district
MeanP_by_district <- listings %>%
  group_by(neighbourhood_cleansed) %>%
  summarise(price_per_p = mean(price_per_p))

#Histogram of mean price

ggplot(MeanP_by_district,
       mapping = aes(x = neighbourhood_cleansed, y = price_per_p)) + geom_col() +
       coord_flip() 
#suburbs have the highest average pricing 

#Boxplot of the median price for each district

ggplot(listings, aes(x = neighbourhood_cleansed, y = price_per_p))  +
  geom_boxplot() +
  scale_y_log10() + coord_flip()
# The range of price for the center districts are most stable, in terms of variability.
# Where as, this is not the case for the suburbs, despite the fact that they have similar median.
# According to the graph, we realize that it is important to know what varaibles predict the 
# price.
  
```

```{r}
#mutate number of listings sorted by area
 neighbourhood_data<-listings %>% 
  group_by(neighbourhood_cleansed) %>% 
  summarize(number_listings=n())

ggplot(neighbourhood_data, aes(x = neighbourhood_cleansed, y = number_listings))  +
  geom_col() + coord_flip()
```
# top four most popular districts: ChaoYang, DongCheng, Haidian, Xichen.

#### albert plot
```{r}
ggplot(listings, aes(x=price_per_p)) +
  geom_histogram()+
  scale_x_log10() # if not looking at the outliers, almost normal distribution
# center around 200-300 rmb per person per night 

ggplot(listings, aes(x=room_type, y =price_per_p))  + 
  geom_boxplot() + 
  scale_y_log10()
# entire home/apt is more expensive than private room then shared room, but not by a lot

```


--------------------------------
# getting rid of N/As

```{r}
colSums(is.na(listings_numerical)) # counting how many N/As in each column
```
Zipcode: 3983; bathrooms: 4, bedrooms:16; beds: 21; square_feet:19980; weekly_price: 19557; monthly_price: 19556; security_deposit: 12360
cleaning_fee: 11737, review_score_rating: 8259, review_scores_accuracy: 8257, review_scores_cleanliness: 8256,  review_scores_checkin:8267
review_scores_communication: 8259, review_scores_location:8281, review_scores_value: 8282, reviews_per_month:7949 

Because almost all entries in this dataset do not have square_feet, weekly_price, monthly_price, defintely dropping those three variables.

# splitting for two models, with and without reviews?

-----------------------
# MICE package 

```{r}
listings_numerical_clean <- listings_numerical%>%
  select(-c(price,square_feet, weekly_price,monthly_price,zipcode,security_deposit,
cleaning_fee, review_scores_rating, review_scores_accuracy, review_scores_cleanliness, review_scores_checkin,
review_scores_communication, review_scores_location, review_scores_value, reviews_per_month, accommodates, latitude, longitude)) #I'm dropping everything （also dropping longtitude, latitude for the ease of regression for now) with N/A, except
#bathrooms, bedrooms, and beds

```
# filling in missing bathrooms, bedrooms and beds
```{r}
tempData <- mice(listings_numerical_clean,m=5,maxit=5,meth='pmm',seed=6210) #citation
summary(tempData)
completed_listings_numerical_clean <- complete(tempData,1)
colSums(is.na(completed_listings_numerical_clean))
```


```{r}
listings_numerical_clean_head <- completed_listings_numerical_clean %>%
  head(5000)

numerical_clean_head <- lm(price_per_p ~ .,data = listings_numerical_clean_head )
summary(numerical_clean_head)
# PI, CI
```

-----------------
Another look at the NAs in the categorical datas

```{r}
colSums(is.na(listings_amenities)) # everybody else is fine except square_feet
```
#regression 

```{r}
listings_amenities_test <- listings_amenities %>%
  select(-c(amenities,accommodates, price))

mamenities_test <- lm(price_per_p ~ ., data = listings_amenities_test)
summary(mamenities_test) # small results
```

————————————————————————————
# Chaoyang

```{r}
listings_chaoyang_amenities <- listings_amenities_test %>%
  filter(neighbourhood_cleansed == "Chaoyang")%>%
  select(-neighbourhood_cleansed)

mod_chaoyang <- lm(price_per_p ~ ., data = listings_chaoyang_amenities)
summary(mod_chaoyang)
```

```{r}
#names(listings_chaoyang)
listings_chaoyang <- listings%>%
  filter(neighbourhood_cleansed == "Chaoyang")%>%
  select(host_response_rate,bathrooms,bedrooms,beds,guests_included,extra_people,minimum_nights,maximum_nights,availability_30,availability_90,availability_365,number_of_reviews,review_scores_rating,review_scores_cleanliness,calculated_host_listings_count,price_per_p)%>% # adding review_scores does not actually raise r or reduce standard error
  mutate(host_response_rate = as.numeric(host_response_rate))%>% # changed host_response_rate into numeric. 
  mice(m=5,maxit=5,meth='pmm',seed=610) # fill in missing N/A bathrooms, bedrooms and beds

listings_chaoyang <- complete(listings_chaoyang,1)
colSums(is.na(listings_chaoyang)) # check for zeros 

mod_chaoyang2 <- lm(price_per_p ~ ., data = listings_chaoyang)
summary(mod_chaoyang2)
```

cor: after running correlation only on numericals, took out availability_60 and host_listings_count

```{r}
completed_listings_chaoyang <-listings %>%
  filter(neighbourhood_cleansed == "Chaoyang")%>%
  select(host_response_rate,bathrooms,bedrooms,beds,guests_included,extra_people,minimum_nights,maximum_nights,availability_30,availability_90,availability_365,number_of_reviews,review_scores_rating,review_scores_cleanliness,calculated_host_listings_count,price_per_p,room_type,instant_bookable, amenities)%>%
  mutate(host_response_rate = as.numeric(host_response_rate))%>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace"))%>%
  select(-amenities) %>%
  mice(m=5,maxit=5,meth='pmm',seed=620) # fill in missing N/A bathrooms, bedrooms and beds

completed_listings_chaoyang <- complete(completed_listings_chaoyang,1)
colSums(is.na(completed_listings_chaoyang))
```

```{r}
mod_chaoyang_full <- lm(price_per_p ~ ., data = completed_listings_chaoyang)
summary(mod_chaoyang_full)
```

```{r}
stepwise_chaoyang <- regsubsets(price_per_p~ ., data = completed_listings_chaoyang, nbest = 1, nvmax = 30, method = "seqrep")
with(summary(stepwise_chaoyang), data.frame(cp, outmat)) #according to smallest cp, pick 18
```

```{r}
mod_chaoyang_18 <- lm(price_per_p ~host_response_rate+bathrooms+bedrooms+beds+guests_included+extra_people+availability_30+availability_90 +number_of_reviews+review_scores_rating+review_scores_cleanliness+room_type+parking+gym+essentials+washer+dryer+heat, data = completed_listings_chaoyang)
summary(mod_chaoyang_18)
```

________________
central districts 

```{r}
central_distrcits <- listings %>%
  filter (neighbourhood_cleansed == "Chaoyang"| neighbourhood_cleansed == "Dongcheng"| neighbourhood_cleansed == "Haidian"| neighbourhood_cleansed == "Xicheng" )%>%
select(host_response_rate,bathrooms,bedrooms,beds,guests_included,extra_people,minimum_nights,maximum_nights,availability_30,availability_90,availability_365,number_of_reviews,calculated_host_listings_count,price_per_p,room_type,instant_bookable, amenities, availability_60,host_listings_count)%>%
  mutate(host_response_rate = as.numeric(host_response_rate))%>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace"))%>%
         select(-amenities)%>%
         mice(m=5,maxit=5,meth='pmm',seed=621)

central_distrcits <- complete(central_distrcits,1)
colSums(is.na(central_distrcits))
```

```{r}
mod_central_distrcits <- lm(price_per_p ~ ., data = central_distrcits)
summary(mod_central_distrcits)
```

```{r}
stepwise_central <- regsubsets(price_per_p~ ., data = central_distrcits, nbest = 1, nvmax = 20, method = "seqrep")
with(summary(stepwise_central), data.frame(cp, outmat)) #according to smallest cp, pick 14
```

```{r}
mod_central_14 <- lm(price_per_p ~host_response_rate+bathrooms+bedrooms+beds+extra_people+availability_30+number_of_reviews+room_type+parking+ac+essentials+washer+dryer, data = central_distrcits)
summary(mod_central_14) 
```


```{r}
suburb <- listings %>%
  filter (neighbourhood_cleansed == "Huairou"| neighbourhood_cleansed == "Mentougou"| neighbourhood_cleansed == "Yanqing")%>%
select(host_response_rate,bathrooms,bedrooms,beds,guests_included,extra_people,minimum_nights,maximum_nights,availability_30,availability_90,availability_365,number_of_reviews,calculated_host_listings_count,price_per_p,room_type,instant_bookable, amenities, availability_60,host_listings_count)%>%
  mutate(host_response_rate = as.numeric(host_response_rate))%>%
  mutate(parking = str_detect(amenities, "park"),
         wifi = str_detect(amenities,"wifi"),
         tv = str_detect(amenities,"TV"),
         ac = str_detect(amenities,"Air conditioning"),
         gym = str_detect(amenities,"Gym"),
         essentials = str_detect(amenities,"Essentials"),
         kitchen = str_detect(amenities,"Kitchen"),
         washer = str_detect(amenities,"Washer"),
         dryer = str_detect(amenities,"Dryer"),
         elevator = str_detect(amenities,"Elavator"),
         heat = str_detect(amenities,"Heating"),
         workspace = str_detect(amenities,"Laptop friendly workspace"))%>%
         select(-amenities)%>%
         mice(m=5,maxit=5,meth='pmm',seed=621)

suburb <- complete(suburb,1)
colSums(is.na(suburb))
```

```{r}
mod_suburb <- lm(price_per_p ~ ., data = suburb)
summary(mod_suburb)
```

```{r}
stepwise_suburb <- regsubsets(price_per_p~ ., data = suburb, nbest = 1, nvmax = 15, method = "seqrep")
with(summary(stepwise_suburb), data.frame(cp, outmat))
```

```{r}
mod_suburb_15 <- lm(price_per_p ~host_response_rate+bathrooms+bedrooms+beds+extra_people+availability_365+calculated_host_listings_count+room_type+availability_60+host_listings_count+gym+essentials+washer+ heat+workspace, data = suburb)
summary(mod_suburb_15)
```
________________
<<<<<<< HEAD
Absolute mean residual for ChaoYang Model, 
=======
Assessing Conditions for models after stepwise:

```{r}
#Assessing Conditions
plot(mod_chaoyang_18, which=c(1,2))
plot(mod_central_14, which=c(1,2))
plot(mod_suburb_15, which=c(1,2))

```

________________
Individual Residual and MSE, CI,PI and onditions for ChaoYang Model

>>>>>>> 3586bbf470b1579224baecd73262c07f9a3666ec
```{r}
means = array(0, 1000)
for (i in 1:1000) {
  #Random Selecting Sample 
ChaoYang_Sample<-sample_n(completed_listings_chaoyang, 1000)
#Sample Model for ChaoYang District 
mod_chaoyang_Sample <- lm(price_per_p ~ ., data =  
ChaoYang_Sample)

#Mean  residual of the first 1000 listings in ChaoYang

means[i]=mean(abs(resid(mod_chaoyang_Sample)))
# median(abs(resid(mod_chaoyang_Sample)))
}

meanRes_chaoyang<-data.frame(means=means)


```

```{r}
median = array(0, 1000)
for (i in 1:1000) {
  #Random Selecting Sample 
ChaoYang_Sample<-sample_n(completed_listings_chaoyang, 1000)
#Sample Model for ChaoYang District 
mod_chaoyang_Sample <- lm(price_per_p ~ ., data =  
ChaoYang_Sample)

# median residual of the first 1000 listings in ChaoYang

median[i]=median(abs(resid(mod_chaoyang_Sample)))
}

medianRes_chaoyang <-data.frame(median=median)
```

#Density plot for Mean and Median Resid
```{r}
densityplot(median,medianRes_chaoyang,main="Median Residual Denisty Plot For ChaoYang",
        xlab="Median Residual",
      )

```



________________
Mean Residual for Central District

```{r}

means = array(0, 1000)
for (i in 1:1000) {
central_distrcits_Sample<-sample_n(central_distrcits, 1000)
#Sample Model for Central District 
mod_central_distrcits_Sample <- lm(price_per_p ~ ., data =central_distrcits_Sample)

#Mean Residual
means[i]=mean(abs(resid(mod_central_distrcits_Sample)))


}

meanRes_central<- data.frame(means=means)



```
#Median Residual For Central District 
```{r}
median = array(0, 1000)
for (i in 1:1000) {
  central_distrcits_Sample<-sample_n(central_distrcits, 1000)
#Sample Model for ChaoYang District 
mod_central_distrcits_Sample <- lm(price_per_p ~ ., data =central_distrcits_Sample)

#Median Residual for central District
  
median[i]=median(abs(resid(mod_central_distrcits_Sample))) }
medianRes_central <- data.frame(median=median)
```

#Density Plot of Mean and Meidan Residual for Central District
```{r}
densityplot(median,medianRes_central,main="Median Residual Denisty Plot For Central",
        xlab="Median Residual",
      )

```

________________
Median Residual for Suburb Model

```{r}
median = array(0, 1000)
for (i in 1:1000) {
#Random Selecting Sample 
suburb_Sample<-sample_n(central_distrcits, 1000)
#Sample Model for ChaoYang District 
mod_suburb_Sample <- lm(price_per_p ~ ., data =suburb_Sample)

#median residual
median[i]=median(abs(resid(mod_suburb_Sample)))
}

medianRes_suburb<- data.frame(median=median)


```
# Density Plot for Suburb Model
```{r}
densityplot(median,medianRes_suburb,main="Median Residual Denisty Plot For Suburb",
        xlab="Median Residual",
      )
```











#Citation

citation for mice: https://datascienceplus.com/imputing-missing-data-with-r-mice-package/
for'polyreg':https://www.analyticsvidhya.com/blog/2016/03/tutorial-powerful-packages-imputing-missing-values/
<<<<<<< HEAD


#### additional code

CI PI for ChaoYang
```{r}
#CI,PI
#predict(mod_chaoyang_full, newdata=data.frame(bedrooms=2,host_response_rate=20), interval="confidence")
#predict(mod_chaoyang_full, newdata=data.frame(bedrooms=2), interval="prediction")  #keep saying that host_response_rate not found..... 

```

```{r}
# data_cleaned <- data_raw %>%  #from albert
#   mutate(
#     price = str_replace_all(price, "\\$", ""),
#     price = str_replace_all(price, ",", ""),
#     price = as.numeric(price)
#     )
#change all factor to numerical in listings_numerical 
#So it kept saying that NAs introduced by coercion when I try to get rid of the dollar sign. 
```


```

```{r}

# listings_numerical_cleaned <- listings_numerical %>%
#   mutate(
#     price = str_replace_all(price, "\\$", ""),
#     price = str_replace_all(price, ",", ""),
#      price = as.numeric(price),
#     weekly_price= as.numeric(weekly_price),
#     monthly_price = as.numeric(monthly_price),
#     security_deposit = as.numeric(security_deposit),
#     cleaning_fee  = as.numeric(cleaning_fee ),
#     extra_people = as.numeric(extra_people),
#     zipcode = as.numeric(zipcode),
#     host_response_rate = as.numeric(host_response_rate)
#     )
  
```
=======
>>>>>>> 3586bbf470b1579224baecd73262c07f9a3666ec
